\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Mari0}

\author{Team 9, Ninetendo
		\\ Jeff Pineda - pinedaj
		\\ Jose Miguel Ballesteros - ballesjm
		\\ David Hobson - hobsondd
}

\date{}

\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2016-09-22 & Jeff Pineda, Jose Ballesteros, David Hobson & Problem statement created\\
2016-09-23 & Jeff Pineda, Jose Ballesteros, David Hobson & Revision\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

Dealing with boredom and finding a way to entertain one's self has been a problem faced by many since the beginning of time. One solution to combating boredom is to play a game. These games can range from a simple chalk game of tic-tac-toe, to tabletop games, and thanks to the invention of computers, video games. As both technology and game design progress, video games can appeal to almost anybody due to the number of genres available. Whether a person is looking for an immersive world and engaging story, a fast paced game of quick reflexes and precise motor skills, or a mentally challenging puzzle, there is a game out there that can appeal to anyone and keep their boredom at bay. Currently, video games are judged critically on various aspects like user interface (UI), graphics, creativity, and innovation.\\
 
Our goal is to recreate Mari0 a video game that combines the best aspects of two of the greatest video games of all time, Super Mario Bros. and Portal. Super Mario Bros. is an early platforming game made by Nintendo with easy mechanics such as jumping on enemies, and collecting coins. Portal is a science fiction puzzle game created by Valve that allows the player to summon portals that the player can move through in order to solve complex problems.\\
 
People can experience boredom in almost any environment, any time and place, so being able to download and run the software on any laptop or desktop computer is ideal. Providing entertainment is important for society because it will prevent the build up of stress. Boredom may lead to a decrease in creativity, imagination and inspiration. If we provide a game that features the best parts from Super Mario Bros. and Portal we will be able to engage the user?s mind in more creative ways.\\
 
The stakeholders are the game's publisher, who have a direct monetary interest in the game, investing money into the marketing, production, and distribution of the game. The game's developers and designers are also stakeholders, applying their skills, experience and giving their time to developing the video game. Another group of stakeholders are the players themselves, since it is their problem that is being addressed. If the game fails to entertain the player, then the publisher and developers have failed to address the players' wants, and thus will lose out on sales.\\

\wss{comment}

\ds{comment}

\mj{comment}

\cm{comment}

\mh{comment}

\end{document}